Clustering Beat-Chroma Patterns in a Large Music Database

### 2010-03-23 Paper/Paper.tex
new figure: freqs, added
caption improved

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.9\columnwidth]{codes1}
\end{center}
\caption{\small{
Most used codes in the codebook in term of frequency of use in the test
set (artist20, see Subsection \ref{ssec:artist}). 
This codebook was of size $200$ and trained on $2$ bars, pattern
size is $12$x$8$. Code in Figure \ref{fig:code} is the $8$th most used
here (second row, third column). 
Numbers display are the index (from most used to least) and in parentheses
the percentage of use in the whole collection times $100$.
There is $71832$ patterns in total in the dataset.
}}
\label{fig:codes1}
\end{figure}

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.7\columnwidth]{freqs}
\end{center}
\caption{\small{
Frequency of use of the patterns in Figure \ref{fig:codes1} on the
artist20 dataset.
There is $71832$ patterns in total in the dataset.
}}
\label{fig:freqs}
\end{figure}

>>>>

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.9\columnwidth]{codes1}
\end{center}
\caption{\small{
Most used codes in the codebook in term of frequency of use in the test
set (artist20, see Subsection \ref{ssec:artist}). 
This codebook was of size $200$ and trained on $2$ bars, pattern
size is $12$x$8$. Code in Figure \ref{fig:code} is the $8$th most used
here (second row, third column). 
Numbers display are the index (from most used to least) and in parentheses
the percentage of use in the whole collection times.
There is $71832$ patterns in total in the dataset.
}}
\label{fig:codes1}
\end{figure}

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.7\columnwidth]{freqs}
\end{center}
\caption{\small{
Frequency of use of the patterns in Figure \ref{fig:codes1} on the
artist20 dataset. 
There is $71832$ patterns in total in the dataset.
Note that all codes were initialized with a random
sample from the training set, some might not just be present in this
test set.
}}
\label{fig:freqs}
\end{figure}
